Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-04 ForegroundSimulations/ms.tex
Update HERA section, add citations
From ff20950 (fgsim):
====================

In eor.bib,

(*) Add few more references

In ms.tex,

(*) Update section 2 on HERA Instrument

The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}. Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}. These instruments have sufficient sensitivity for a statistical detection of the EoR signal via estimating the spatial power spectrum of the redshifted H{\sc i} temperature fluctuations \citep{bea13,thy13}. These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA; DeBoer~et~al.~2015) and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA). These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} during the EoR.

@@

DeBoer~et~al.(2016)

@@

The High Frequency Structural Simulator (HFSS) was used to model the dish and its angular response used in this study. The HFSS model used prime focus optics with a 14~m faceted parabola with a spar f/D ratio of 0.32.  The model has a 1~m central hole in the aluminum surface which is filled with a dielectric material similar to dry soil. The feed used a full PAPER dipole inside of a cylindrical backplane, the backplane is modeled as an aluminum surface. For the metal parts of the dipole, the discs were modeled as aluminum at the actual size, and the arms and terminals were modeled as copper. Dielectric stand-offs and supporting members were included. For the calculations, one pair of arms was excited using a modal port. These models cover a frequency range of 100--200~MHz in intervals of 1~MHz. Refer to DeBoer~et~al.~(2016) for a complete description of the dish model.

@@

One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument. Patra~et~al.~2015 (in preparation) and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed. Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam. In this section, we provide cosmologically motivated upper limits on instrument systematics caused by these two types of reflections.

@@

The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections. This depends sensitively on the chosen $k_\parallel$ modes. For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$. Measurements by Patra et al. (2016) for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.

>>>>

The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}. Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Donald~C.~Backer Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}. These instruments have sufficient sensitivity for a statistical detection of the EoR signal via estimating the spatial power spectrum of the redshifted H{\sc i} temperature fluctuations \citep{bea13,thy13}. These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} \citep[HERA;][]{deb16} and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA). These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} during the EoR.

@@

\citet{deb16} describe the HERA instrument in detail. Here, we provide a brief summary.

The primary science goal of HERA is to widen our understanding of the first stars, galaxies, and black holes, and their role in driving reionization. Through power-spectral measurements of the redshifted 21cm line of H{\sc i} in the primordial IGM, HERA aims to directly constrain the topology and evolution of reionization, opening a unique window into the complex astrophysical interplay between the first luminous objects and their environments. HERA builds on the advances of first-generation 21cm EoR experiments, particularly PAPER, MWA, the MIT EoR experiment \citep[MITEoR;][]{zhe14} and the Experiment to Detect the Global EoR Step \citep[EDGES;][]{bow10}.

HERA will deploy 14~m fixed zenith-pointing parabolic dishes that strike an optimal balance between sensitivity and systematics. The large collecting area of a HERA element yields $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.

320 core elements of HERA will be arranged in a compact hexagonal grid, split into three displaced segments to cover the $uv$-plane with sub-element sampling density. The core will be supplemented by 30 additional outrigger elements to tile the $uv$-plane with instantaneously complete sub-aperture sampling out to $250\lambda$ and complete aperture-scale sampling out to $350\lambda$ (at 150~MHz). The layout and its advantages are discussed in \citet{dil16}.

In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout. Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.

@@

The High Frequency Structural Simulator (HFSS) was used to model the dish and its angular response used in this study. The HFSS model used prime focus optics with a 14~m faceted parabola with a spar f/D ratio of 0.32.  The model has a 1~m central hole in the aluminum surface which is filled with a dielectric material similar to dry soil. The feed used a full PAPER dipole inside of a cylindrical backplane, the backplane is modeled as an aluminum surface. For the metal parts of the dipole, the discs were modeled as aluminum at the actual size, and the arms and terminals were modeled as copper. Dielectric stand-offs and supporting members were included. For the calculations, one pair of arms was excited using a modal port. These models cover a frequency range of 100--200~MHz in intervals of 1~MHz. Refer to \citet{deb16} for a complete description of the dish model.

@@

One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument. \citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed. Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam. In this section, we provide cosmologically motivated upper limits on instrument systematics caused by these two types of reflections.

@@

The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections. This depends sensitively on the chosen $k_\parallel$ modes. For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$. Measurements by \citet{pat16} for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
